Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-08 docs/evol.tex
corrections - after dds' comments

% In the rest of this paper we
% describe the processing of our data and our experiment (Section \ref{sec:meth}),
% present and discuss the results we obtained (Section \ref{sec:res}),
% outline related work (Section \ref{sec:rel}),
% and end up with a conclusion and directions for future work (Section \ref{sec:con}).

@@

To examine {\it Linus's Law} in relation to the rate of the
security bugs~\cite{MW10}, and highlight the
{\it domino effect}~\cite{TH04} we did the
following: during the experiment we retrieved the
dependencies of every version. Based on this information we created a graph
that represented the snapshot of the Maven repository. The
nodes of the graph represented the versions and the vertices their dependencies.
The graph was not entirely accurate. For instance, if
a dependency was pointing only to a project (and not to a specific version), we chose to
select the latest version found on the repository. Also, this graph is not
complete. This is because there were missing versions.
% Practically, the corresponding {\it pom}, or {\it war} files existed on the
% repository, but the {\sc jar} file did not.
From the 565,680 vertices, 191,433
did not point to a specific version while 164,234 were pointing to missing ones.
The graph contained 80,354 nodes. Obviously, the number does not correspond to
the number of the total versions (see Section~\ref{sec:data}). This is because
some versions did not contain any information about their dependencies so they
are not represented in the graph. After creating the graph, we ran the PageRank
algorithm~\cite{BP98} on it and retrieved all PageRanks for every node. Then we
examined the security bugs of the fifty most popular nodes based on their PageRank.
Contrary to Linus's Law, thirty three of them contained bugs coming from the
{\it Security Low} subcategory, while two of them contained severe bugs.
Twenty five of them were latest versions at the time. This also highlights
the domino effect. No matter how well a programmer secures a software component
it won't matter if he or she is using vulnerable code fragments coming
from another library.

@@

@@

\begin{figure*}[t]
  \centering
  \includegraphics[scale=0.4]{bugdiffs}
  \caption{Histograms of the time, measure in versions, it takes for a
    bug to be closed. }
  \label{fig:bugdiffs}
\end{figure*}

>>>>

In the rest of this paper we
describe the processing of our data and our experiment (Section \ref{sec:meth}),
present and discuss the results we obtained (Section \ref{sec:res}),
outline related work (Section \ref{sec:rel}),
and end up with a conclusion and directions for future work (Section \ref{sec:con}).

@@

{\it Linus's Law} states that ``given enough eyeballs, all bugs are shallow".
To examine Linus's Law in relation to the rate of the
security bugs~\cite{MW10}, and highlight the
{\it domino effect}~\cite{TH04} we did the
following: during the experiment we retrieved the
dependencies of every version. Based on this information we created a graph
that represented the snapshot of the Maven repository. The
nodes of the graph represented the versions and the vertices their dependencies.
The graph was not entirely accurate. For instance, if
a dependency was pointing only to a project (and not to a specific version), we chose to
select the latest version found on the repository. Also, this graph is not
complete. This is because there were missing versions.
% Practically, the corresponding {\it pom}, or {\it war} files existed on the
% repository, but the {\sc jar} file did not.
From the 565,680 vertices, 191,433
did not point to a specific version while 164,234 were pointing to missing ones.
The graph contained 80,354 nodes. Obviously, the number does not correspond to
the number of the total versions (see Section~\ref{sec:data}). This is because
some versions did not contain any information about their dependencies so they
are not represented in the graph. After creating the graph, we ran the PageRank
algorithm~\cite{BP98} on it and retrieved all PageRanks for every node. Then we
examined the security bugs of the fifty most popular nodes based on their PageRank.
Contrary to Linus's Law, thirty three of them contained bugs coming from the
{\it Security Low} subcategory, while two of them contained severe bugs.
Twenty five of them were latest versions at the time. This also highlights
the domino effect. No matter how well a programmer secures a software component
it won't matter if he or she is using vulnerable code fragments coming
from another library.

@@

Here, we present our key findings concerning the evolution of security bugs.

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\textwidth]{bugdiffs}
  \caption{Histograms of the time, measure in versions, it takes for a
    bug to be closed. }
  \label{fig:bugdiffs}
\end{figure*}
